Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-07-31 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:07:30	21:57:57	(Thu30.Jul)
la2pdf commit - 2015:07:31	14:36:31	(Fri31.Jul)
la2pdf commit - 2015:07:31	15:10:13	(Fri31.Jul)

@@

% \newpage
\section{Results and Discussion}

@@

\begin{figure*}%\centering%
\includegraphics[width=.5\linewidth]{gfx/calc_kaiser_3dB.pdf}%
\caption{Steering within -3dB for each window}\label{windows_steering}
\end{figure*}

\newpage
\begin{figure*}%\centering%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic_bounds.pdf}%
\caption{Window parameter boundaries. Oversampled image, 19x20 windows.}\label{oversampling_mosaic_bounds}
\end{figure*}

\begin{figure*}%\centering%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic_bounds_lca_windows_beta.pdf}%
\caption{Window parameter boundaries. Oversampled image, 19x20 windows.}\label{oversampling_mosaic_bounds}
\end{figure*}

>>>>

- Find window function
- Determine bounds
- Determine oversampling need
- Compare image quality

@@

\newpage
\section{Results and Discussion}

Before we started designing our LCA window database, we wanted to study the window resposes that a robust MVDR typically computes. For this we selected a scene of the oil tanker wreck Holmengraa, which lies at a slanted seabed at nearly 100m\;depth. A sectorscan image of a single ping of data collected by the HISAS1030 syntetic aperture sonar is shown in \Fig{mvdr_selected_windows}, along with the window responses MVDR typically chooses in shadow, speckle and highlight regions in this image. A fairly agressive yet stable set of parameters for MVDR where used; subarray size $L=16$, temporal averaging of $K=1$, and $d=1\%$ of diagonal loading.

@@

\begin{figure*}[tbhp!]%\centering%
\includegraphics[width=.5\linewidth]{gfx/calc_kaiser_3dB.pdf}%
\caption{Steering within -3dB for each window}\label{windows_steering}
\end{figure*}

\newpage
\begin{figure*}[tbhp!]%\centering%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic_bounds.pdf}%
\caption{Window parameter boundaries. LCA images using an oversampled image and a relatively large window database with $N_\beta=20$ window types, each steered $N_\phi=19$. }\label{oversampling_mosaic_bounds}
\end{figure*}

\begin{figure*}[tbhp!]%\centering%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic_bounds_lca_windows_beta.pdf}%
\caption{Window parameter boundaries. Oversampled image, 19x20 windows.}\label{oversampling_mosaic_bounds}
\end{figure*}

\newpage

What's wrong here?

\begin{figure*}[tbhp!]%\centering%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic.pdf}%
\caption{Window parameter boundaries. Oversampled image, 19x20 windows.}\label{oversampling_mosaic}
\end{figure*}
